Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-04 doc/main_jfm.tex
updates

The preliminary test of the proposed model using the integral equation method is the numerical validation in Jeffery orbits of single ellipsoidal particle under a shear flow $\dot x = \dot\gamma y$ where $\dot\gamma$ is the shear rate. An ellipsoidal particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\chi = 0^\circ$. Based on the theoretical Jeffery orbits with respect to the target angle $\Theta(t)$,

>>>>

The preliminary test of the proposed model using the integral equation method is the numerical validation in Jeffery orbits of single ellipsoidal particle under a shear flow $\dot x = \dot\gamma y$ where $\dot\gamma$ is the shear rate. An ellipsoidal particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\Theta = 0^\circ$. Based on the theoretical Jeffery orbits with respect to the target angle $\Theta(t)$,
